---
title: "Finite Sample Porperties of Maximum Likelihood Estimators of SLS-AGARCH(1,
  1) Model Parameters"
output: pdf_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo=FALSE, cache=FALSE}
library(SLSAGARCH)
library(SimStudySLSAGARCH)
library(fst)
library(dplyr)
library(rsimsum)
```

# Simulation Design

The package contains data simulated from nine different SLS-AGARCH(1, 1) DGPs with hyperbolic secant distributed innovations. The parameters of the nine models are stored in the data frame `parameters`.

```{r}
data("sls_sech_spec")
data("parameters")

parameters
```

We will refer to the different DGPs as scenarios. For each scenario, 10000 realisations of length $n \in \{ 250, 500, 750, 1000, 1250, 2500 \}$ were generated. The parameters $\lambda$ and $rho$ vary across scenarios, whereas $h_0 = 1,$ $\alpha = 0.075$ and $beta = 0.85$ for all DGPs. The value of $omega = 1 - P$ across all scenarios, such that the unconditional variance of each DGP is one.

# Estimation

## Scenario 1: $\omega = `r parameters$omega[1]`,\ \lambda = `r parameters$lambda[1]`, \ \rho = `r parameters$rho[1]`$

Load the data for Scenario 1:
```{r importScenario01}
scenario_01 <- scenario_files(
  path = "scenario_01.fst") |>
  fst::read.fst()
scenario_01 <- split.data.frame(
  scenario_01, f = scenario_01$n)
# Convert to matrices for use with `fit_many`
scenario_01 <- lapply(scenario_01, function(x) {
  as.matrix(x[, -1 * 1:3])
})
```

We will now apply `fit_many` to estimate an SLS-AGARCH(1, 1) model for each realisation.

```{r estimateScenario01}
estimates_01 <- foreach(mat = scenario_01, .combine = "bind_rows") %do% {
  progressr::with_progress(
    fit_many(sls_sech_spec, param = as.vector(parameters[1, ]), ymat = mat, strategy = "multisession")
  )
}
estimates_01$true <- estimates_01$true |> unlist()
estimates_01 |>
  dplyr::as_tibble() |>
  dplyr::mutate(
    Simulation = as.factor(Simulation),
    par = as.factor(par)) |>
  dplyr::rename(
    "Estimate" = "est", "Parameter" = "par",
    "True" = "true", "SE" = "se") |>
  as.data.frame() |>
  fst::write_fst(path = "inst/extdata/estimates_01.fst", compress = 25)
rm(list = c("scenario_01", "estimates_01"))
```

